\subsection{Overview}
    The computation of the correlation function on one gauge configurations can be broken down into the following steps
    \begin{enumerate}
        \item computation of $N$ eigenvectors
        \item generation of $T \times 4 \times N$ sources
        \item computation of as many inversions as there are sources
        \item calculation of the perambulator and distilled gamma matrix
        \item computation of the correlation function
    \end{enumerate}
    This work builds on the contraction code written by members of Marc Wagner's group, code by Jan Kruse and the aforementioned \verb+tmLQCD+ package. For documentation about steps 1 through 3 please see \cite{bachelor_thesis_jan}.



\subsection{Modules}
    The following modules written in C++11 were added to the existing contraction code in \\\verb+.../distillation/+. Every module consists of a \verb+main.cpp+, a \verb+module.h+ and a \verb+module.cpp+ file. The documentation of each function can be found in the corresponding .h file.  
    \begin{itemize}
        \item \verb+perambulator/+: Calculates the perambulator using the sources and inverted sources.
        \item \verb+distilled_gamma/+: Computes the distilled gamma matrix given the calculated eigenvectors.
        \item \verb+correlator_trace/+: Computes the correlator for a given perambulator and distilled gamma matrix.
    \end{itemize}
    
    \noindent
    In addition to the above a \verb+MultiVector+ class has been written which can store a matrix of arbitrary dimension. Such a matrix can then be written to the disk. The definition of this class can be found in \verb+helper/multivector.hpp+. It is used to store the perambulator, distilled gamma matrix and correlator trace.
    
    For a more technical documentation see the provided \verb+README+ files and comments inside the source code.
    
    \subsubsection{Computation of the perambulators}
        This program computes the perambulator for all sources and inverted sources in two directories.
        The sources and the inverted sources \emph{have to be} in the format
        \begin{verbatim}
source.CONF-ID.time##.vec##.spin#
source.CONF-ID.time##.vec##.spin#.CONF-ID.00.inverted\end{verbatim}
        respectively. Here \verb+#+ stands for a digit and \verb+CONF-ID+ is usually a 4-digit number. The program will read in all sources and inverted sources for one pair $(k,k')$ into memory at once. Hence running the program needs, for the gauge configurations used, about 48GB of RAM.\\
        
        \noindent
        The program can be started by calling
        \begin{verbatim}
./perambulator path-to-sources path-to-inverted-sources conf_id
               path-to-target-dir num_vec T L\end{verbatim}
        where \verb+num_vec+ is the total number of eigenvectors $N$, \verb+T+ is the time dimension and \verb+L+ the spacial dimension of the lattice. Both \verb+path-to-sources+ and \verb+path-to-inverted-sources+ are paths to the directory where the sources and inverted sources live. The perambulator will be saved to the directory given by \verb+path-to-target-dir+ in the format
        \begin{verbatim}
perambulator.CONF-ID.num_vec##.time##\end{verbatim}
        using the \verb+MultiVector+ storage type mentioned earlier.
    
    \subsubsection{Computation of the distilled gamma matrix}
        This program computes the distilled gamma matrix for a given eigenvector. The gamma matrix $\Gamma$ can be changed inside the source code. The distilled gamma matrix will be saved in the format
        \begin{verbatim}
gamma.CONF-ID.num_vec##.time##\end{verbatim}
        again using the \verb+MultiVector+ storage type.\\
        The program can be started by calling
        \begin{verbatim}
./gamma path-to-ev conf_id path-to-target-dir num-vec T L\end{verbatim}
        \verb+path-to-ev+ is the path to the file which holds the eigenvectors.
        
    \subsubsection{Computation of the correlation function}
        To calculate the correlation function call
        \begin{verbatim}
./trace path-to-gamma-matrix path-to-perambulator conf_id 
        path-to-target-dir num_vec T\end{verbatim}
        Here \verb+path-to-gamma-matrix+ and \verb+path-to-perambulator+ are the paths to the files holding the distilled gamma matrix and perambulator calculated earlier. The correlator will be saved in the format
        \begin{verbatim}
trace.CONF-ID.num_vec##.time##\end{verbatim}
        This file will contain all $T^2$ elements of the correlation function. To read the trace and calculate the mean values for every $\Delta t$ run
        \begin{verbatim}
./trace -r path-to-trace T\end{verbatim}
        This will print all values in the format 
        $$\Delta t\ real(C)\ imag(C)$$
        where $C$ is the correlation function. The output of this operation is the basis for the results in section \ref{section:results}.
        
    \subsubsection{Python control script}
        In addition to the modules already mentioned a python script to control the simulation was written. It can find all files necessary for the simulation and can set up slurm job scripts (which are necessary on the \textit{FUCHS} super computer) automatically. The script can be found inside the folder \verb+.../distillation/scripts/+ alongside its documentation. To start the script run
        \begin{verbatim}
./run.py\end{verbatim}
        The script will walk you through the setup process. It is written in python version 3.6.
    